Does stomatal patterning in amphistomatous leaves minimize the CO$_2$ diffusion path length within leaves?

### 2024-03-05 ms/ms.Rmd
added zenodo url to ms

Custom scripts are available on a GitHub repository (https://github.com/cdmuir/stomata-spacing) and archived on Zenodo: https://doi.org/XXXX Raw data are deposited on Dryad: https://doi.org/10.5061/dryad.44j0zpcn6

>>>>

Custom scripts are available on a GitHub repository (https://github.com/cdmuir/stomata-spacing) and archived on Zenodo: https://doi.org/10.5281/zenodo.10775962 Raw data are deposited on Dryad: https://doi.org/10.5061/dryad.44j0zpcn6
